---
title: "Predicting stock prices using autoregressive models"
author: "Felix Gallagher"
date: '`r format(Sys.time(), "%d, %M, %Y")`'
output:
  reprex::reprex_document:
    venue: "gh"
    advertise: FALSE
    session_info: TRUE
    style: TRUE
    comment: "#;-)"
    tidyverse_quiet: FALSE
    std_out_err: TRUE
knit: reprex::reprex_render
---

## Set up

The code block loads in the relevant functions and downloads the data from the tidytuesday website.

```{r}

source("utils.R")
check_packages(required_packages, install_packages = TRUE)
lapply(required_packages, require, character.only = TRUE, quietly = TRUE)

folder_dir <- "stock_prices"
source(file.path(here(), folder_dir, "funcs.R"))

config <- yaml::yaml.load_file(file.path(here(), "catalogue.yml"))$stock_prices
prices <- load_data(config$prices_url)
companies <- load_data(config$companies_url)
data_raw <- dplyr::left_join(companies, prices)
View(data_raw)
```

Now we create some of our own variables.
```{r}
data_full <- process_stock_data(data_raw)
```

We can generate a quick plot of the prices over time to look at the data.

```{r}
library(ggplot2)
plot <- quick_line_plot(
    data_full,
    x_col = "date",
    y_col = "avg_price",
    id_cols = "company",
    title = "Price of major tech stocks over time",
    x = "Time",
    y = "Average daily price",
    color = "Company"
)
print(plot)
```

Now we can build an autoregressive model using lagged variables and a linear regression.
```{r}
cols_to_model <- c("date", "company", "avg_price")

# set autoregressive order
p <- 4

# drop unnecessary columns
data_subset <- data_full |>
    dplyr::select(all_of(cols_to_model))

# split dataset into train and eval
train_test_lst <- split_train_test(
    data_subset,
    test_prop = 0.05,
    strata = "company",
    mode = "latest"
)

ar_data <- create_p_lags(train_test_lst$train, "company", "avg_price", p)
eval <- create_p_lags(train_test_lst$test, "company", "avg_price", p)
input_cols <- missing_items(colnames(ar_data), c("avg_price", "company", "date"))

ar_model <- ar_p("avg_price", input_cols, p)

# fit model to training data
ar_fit <- ar_model |>
    parsnip::fit(data = ar_data)
```

Now that we have trained the model, we can get some estimates of its accuracy on the evaluation set.

```{r}
predictions <- get_predictions(
    ar_fit,
    eval,
    "avg_price",
    get_metrics = TRUE,
    metrics = c("mse")
)

rmse <- (predictions$metric_df$mse) ^ 0.5
print(rmse)
```